### 2018-10-12 paper/complexity.tex
update - still incomplete

Given an alphabet $\Sigma$ of size $\card{\Sigma} = n\ge 2$, define
a collection of subsets of $\Sigma$ by
\[
{\cal C} = \{ A\subseteq\Sigma~|~\card{A} = n - \lfloor\frac{n}{2}\rfloor + 1 \}.
\]
%
With this choice of ${\cal C}$, define
\begin{equation}\label{eq:pmax}
\pmax = \Intchoice_{A\in{\cal C}} e:A\then \pmax
\end{equation}
%
The important properties of $\pmax$ are summarised in the following lemma.
%
\begin{lemma}\label{lemma:pmax}
Given alphabet $\Sigma$ with cardinality $\card{\Sigma} = n\ge 2$,
process $\pmax$ fulfils
%
\begin{eqnarray}
{}[\pmax/s]^0 & = & \Sigma \quad\text{for all $s\in \Sigma^*$}
\label{eq:pmaxa}
\\
\trc(\pmax) & = & \Sigma^*
\label{eq:pmaxb}
\\
\minaccs(P/s) & = & {\cal C} \quad\text{for all $s\in \Sigma^*$}
\label{eq:pmaxc}
\\
\minhits(P/s) & = & \minhits({\cal C}) \quad\text{for all $s\in \Sigma^*$}
\label{eq:pmaxe}
\\
\card{\minhits(P/s)} & = & \binom{n}{\lfloor\frac{n}{2}\rfloor} 
\quad \text{for all $s\in \Sigma^*$}
\label{eq:pmaxd}
\end{eqnarray}
\end{lemma}
\begin{proof}
 Since  
$
\bigcup_{A\in{\cal C}} A = \Sigma
$
by construction of ${\cal C}$, $[\pmax]^0 = \Sigma$. Since $\pmax/e = \pmax$ for all
$e\in\Sigma$, this proves statements (\ref{eq:pmaxa}) and (\ref{eq:pmaxb}).
The internal choice construct used in the specification of $\pmax$ implies
$\minaccs(\pmax) = {\cal C}$. Again, $\pmax/e = \pmax$ for all
$e\in\Sigma$ implies $\minaccs(\pmax/s) = {\cal C}$ for all traces of $\pmax$, so this shows (\ref{eq:pmaxc}). Statement (\ref{eq:pmaxe}) is a direct consequence
of (\ref{eq:pmaxc}).

Let $H$ be any minimal hitting set of ${\cal C}$. Then
$H$ contains at least $\lfloor{\frac{n}{2}}\rfloor$ elements, because
otherwise $\card{\Sigma\setminus H} > n-\lfloor{\frac{n}{2}}\rfloor$, and any
subset $A\subseteq \Sigma\setminus H$ with cardinality
$n-\lfloor{\frac{n}{2}}\rfloor+1$  would be contained in ${\cal C}$, but satisfy
$A\cap H=\varnothing$. Since
$\lfloor{\frac{n}{2}}\rfloor+n-\lfloor{\frac{n}{2}}\rfloor+1=n+1$, we
conclude
 that any $\lfloor{\frac{n}{2}}\rfloor$-element subset of $\Sigma$
 intersects  every element of ${\cal C}$.  Therefore, every minimal hitting set of ${\cal C}$ has exactly $\lfloor{\frac{n}{2}}\rfloor$ elements,
so $\card{\minhits({\cal C})} = \binom{n}{\lfloor{\frac{n}{2}}\rfloor}$. This 
shows  (\ref{eq:pmaxd}) and completes the proof.
\xbox
\end{proof}

The test cases $U_F(j)$ generated from $\pmax$ have the structure
\begin{eqnarray*}
\label{eq:UFP}
U_F(j) & = & U_F(j,0,\ii n)
\\
U_F(j,k,n) & = &   (k < j) \& \big(e:\Sigma   \then U_F(j,k+1,t(n,e) \big)
\\ & & \extchoice  
\\ & & (k = j) \& \big( \Intchoice_{H\in\minhits({\cal C})} (e:H   \then \epass \then\Stop   )  \big)
\end{eqnarray*}

>>>>

% -----------------------------------------------------------------------------
\subsubsection*{Process Definition and Basic Properties}
Given an alphabet $\Sigma$ of size $\card{\Sigma} = n\ge 2$, define
a collection of subsets of $\Sigma$ by
\[
{\cal C} = \{ A\subseteq\Sigma~|~\card{A} = n - \lfloor\frac{n}{2}\rfloor + 1 \}.
\]
%
With this choice of ${\cal C}$, define
\begin{equation}\label{eq:pmax}
\pmax = \Intchoice_{A\in{\cal C}} e:A\then \pmax
\end{equation}
%
The important properties of $\pmax$ are summarised in the following lemma.
%
\begin{lemma}\label{lemma:pmax}
Given alphabet $\Sigma$ with cardinality $\card{\Sigma} = n\ge 2$,
process $\pmax$ fulfils
%
\begin{eqnarray}
{}[\pmax/s]^0 & = & \Sigma \quad\text{for all $s\in \Sigma^*$}
\label{eq:pmaxa}
\\
\trc(\pmax) & = & \Sigma^*
\label{eq:pmaxb}
\\
\minaccs(P/s) & = & {\cal C} \quad\text{for all $s\in \Sigma^*$}
\label{eq:pmaxc}
\\
\minhits(P/s) & = & \minhits({\cal C}) \quad\text{for all $s\in \Sigma^*$}
\label{eq:pmaxe}
\\
\card{\minhits(P/s)} & = & \binom{n}{\lfloor\frac{n}{2}\rfloor} 
\quad \text{for all $s\in \Sigma^*$}
\label{eq:pmaxd}
\\
\card{H} & = & \lfloor\frac{n}{s}\rfloor \quad \text{for all $H\in {\cal C}$}
\label{eq:pmaxf}
\end{eqnarray}
\end{lemma}
\begin{proof}
 Since  
$
\bigcup_{A\in{\cal C}} A = \Sigma
$
by construction of ${\cal C}$, $[\pmax]^0 = \Sigma$. Since $\pmax/e = \pmax$ for all
$e\in\Sigma$, this proves statements (\ref{eq:pmaxa}) and (\ref{eq:pmaxb}).
The internal choice construct used in the specification of $\pmax$ implies
$\minaccs(\pmax) = {\cal C}$. Again, $\pmax/e = \pmax$ for all
$e\in\Sigma$ implies $\minaccs(\pmax/s) = {\cal C}$ for all traces of $\pmax$, so this shows (\ref{eq:pmaxc}). Statement (\ref{eq:pmaxe}) is a direct consequence
of (\ref{eq:pmaxc}).

Let $H$ be any minimal hitting set of ${\cal C}$. Then
$H$ contains at least $\lfloor{\frac{n}{2}}\rfloor$ elements, because
otherwise $\card{\Sigma\setminus H} > n-\lfloor{\frac{n}{2}}\rfloor$, and any
subset $A\subseteq \Sigma\setminus H$ with cardinality
$n-\lfloor{\frac{n}{2}}\rfloor+1$  would be contained in ${\cal C}$, but satisfy
$A\cap H=\varnothing$. Since
$\lfloor{\frac{n}{2}}\rfloor+n-\lfloor{\frac{n}{2}}\rfloor+1=n+1$, we
conclude
 that any $\lfloor{\frac{n}{2}}\rfloor$-element subset of $\Sigma$
 intersects  every element of ${\cal C}$.  Therefore, every minimal hitting set of ${\cal C}$ has exactly $\lfloor{\frac{n}{2}}\rfloor$ elements; this shows (\ref{eq:pmaxf})
and $\card{\minhits({\cal C})} = \binom{n}{\lfloor{\frac{n}{2}}\rfloor}$. The latter 
shows  (\ref{eq:pmaxd}) and completes the proof.
\xbox
\end{proof}

% -----------------------------------------------------------------------------
\subsubsection*{Test Cases of $\pmax$}
The test cases $U_F(j)$ generated from $\pmax$ 
can never enter branch (\ref{eq:ufa}), because $\pmax/s$ has initials $\Sigma$ for
all traces $s\in\trc(\pmax)$ according to Lemma~\ref{lemma:pmax}, (\ref{eq:pmaxa}).
Moreover, they can never enter branch (\ref{eq:ufb}), because $\minhits(\pmax/s)$
is never empty according to Lemma~\ref{lemma:pmax}, (\ref{eq:pmaxd}).
Finally, the minimal hitting sets used to probe the SUT at the end of a
non-blocking  test execution are always the hitting sets of ${\cal C}$ 
according to Lemma~\ref{lemma:pmax}, (\ref{eq:pmaxe}).
This results in a test case structure
\begin{eqnarray*}
\label{eq:UFP}
U_F(j) & = & U_F(j,0,\ii n)
\\
U_F(j,k,n) & = &   (k < j) \& \big(e:\Sigma   \then U_F(j,k+1,t(n,e) \big)
\\ & & \extchoice  
\\ & & (k = j) \& \big( \Intchoice_{H\in\minhits({\cal C})} (e:H   \then \epass \then\Stop   )  \big)
\end{eqnarray*}

When considering the number of test executions to be performed by 
$U_F(j)$ against some SUT $Q$ for all $j=0,\dots,pq-1$, the maximal number of 
test executions is only reached if $Q$ is a correct refinement of the reference
process or if it fails in the very last execution of the very last $U_F(j)$ 
executed against $Q$. If an erroneous behaviour of $Q$ is revealed before this
very last execution, the test suite is stopped and $Q$ is fixed before
executing the suite again.
Therefore, we consider only correct SUTs $Q$ when determining the
maximal number of executions that can be executed.

For the  $U_F(j)$ generated from $\pmax$, the number of test executions
 to be performed is maximal if $\pmax\lessdet_F Q$ and 
$\trc(Q) = \Sigma^*$. In such a situation, no test execution blocks early, because
$Q/s$ can always engage into some $e\in\Sigma$   while $\#s<j$ and will never block
in the last step when $\#s = j$ and a hitting set $H\in\minhits({\cal C})$ is 
offered by the test case. The resulting number of executions is
%
\begin{equation}
\label{eq:maxexec}
\card{\Sigma}^{j}\cdot \binom{n}{\lfloor\frac{n}{2}\rfloor}\cdot \lfloor\frac{n}{2}\rfloor,
\end{equation}
%
because all traces up to length $j$ can be executed with $U_F(j)$ entering branch
(\ref{eq:ufc}), and each of these traces is followed by one event
from each of the hitting sets of ${\cal C}$, and each of these hitting sets 
contains $\lfloor\frac{n}{2}\rfloor$ elements.

The number of executions specified in (\ref{eq:maxexec}) is indeed maximal for
all reference processes $P$ fulfilling $\minhits(P/s)\neq\varnothing$ for all
traces $s$. All these processes can never enter branch (\ref{eq:ufb}), and,
if an execution with an SUT entered branch (\ref{eq:ufa}), this would only lead to early termination of the whole test suite, because a failure has been detected.
As a consequence, $\card{\Sigma}^{j}$ is the maximal number of traces to be executed 
up to length $j$, and from Theorem~\ref{th:sperner} we know that the number
$\binom{n}{\lfloor\frac{n}{2}\rfloor}$ of hitting sets to be tested at the end of each trace of length $j$ is already maximal.
